Cultural evolutionary dynamics with prestige bias

### 2023-01-02 ms/ms.tex
addressed TODOs

% TODO add definition of success bias and some reference to a study demonstrating it in humans or other animals.
Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough, % TODO enough for what?
even if success is measured accurately.

>>>>

A very common bias in the literature is \textit{success bias}. Success bias refers to the tendency for certain cultural traits or behaviors to spread and become more common in a population simply because they have been successful in the past. Success in that regard is defined by each individual trait, for example, a successful manifestation is a ping pong-player who won many games, tournaments, didn't lose much, etc..
\citet{prestige_cultural_learning} describe a definition for success, as well as skill and prestige bias, and their differences.
Indeed, in a tournament between learning strategies conducted by \citet{strategiesPaper}, most winner strategies included a mixture of success-biased social learning and individual learning, implying that success-biased learning is a good strategy, but that by itself it is not enough to best other strategies, even when success is measured accurately.
